---
title: "Introduction to R: Assignment"
description: |
  This assignment accompanies the "Introduction to R" tutorial session for MCom (Economics) students attending the Intensive Statistics course at Stellenbosch University (2024).
author: Wihan Marais
date: 2024-01-24
output:
  distill::distill_article:
    self_contained: false
    highlight: breezedark
    highlight_downlit: true
    toc: true
    toc_float: true
    css: extras/style.css
preview: images/rstudio_logo.png
categories:
  - Intensive Statistics
  - R
  - Teaching
base_url: "https://www.wihanza.com/"
draft: false
---

```{r setup, include=FALSE}
gc()
rm(list = ls())

knitr::opts_chunk$set(echo = FALSE, cache = FALSE, dpi = 300, eval = TRUE)
options("huxtable.knitr_output_format" = "html")
```

*This assignment accompanies the [Introduction to R: Tutorial](https://www.wihanza.com/posts/2024-01-23-introduction-to-r/) presented on 23 January 2024.*

*Download the materials needed to complete this assignment [here](assignment_materials.zip).*

*This post was last updated on `r format(Sys.time(), '%d %B %Y')`.*


## Task 1

- Open R Studio and create a new project in which you will complete the assignment.

- Ensure that you are working from the new project and download the necessary assignment materials using [this link](assignment_materials.zip). Extract the `data` folder from the compressed folder you have downloaded and copy it to your root directory.

> **Hint:** Run `getwd()` in your console to check the file path of your working directory.

- Create a new R Script and save it as `[yourstudentnumber].R` in your directory. Write and execute the code necessary to complete the rest of the assignment in this R Script.

## Task 2

- Using comments, create headings in your script for each of the subsequent tasks. Write your code under the appropriate headings.

> **Hint:** In `.R` files, comments are created using the pound sign, i.e., `#`.

- Load the `pacman` package using `install.packages("")` (if necessary) and `library()`.

- Install/load the following packages using the `pacman` package:
  - `tidyverse`
  - `huxtable`
  - `fixest`

```{r task2}
library(pacman)
p_load(tidyverse, huxtable, fixest)
```


## Task 3

1. Read the `ts_data.csv` file and store it as a data frame in your Global Environment.

2. Use the `tidyverse` syntax (`%>%`) and `mutate()` to ensure that the `Year` column is of the class `date`.

3. Ensure that the data frame is arranged chronologically. 

4. Subset/filter the data frame to contain only observations for France or Italy between the years 1985-2010.

> **Hint:** When filtering, use the AND (`&`) and OR (`|`) operators.

5. Using `ggplot()`, create a line and scatter plot for the time series `ln_consump_pc` of both countries in the same figure. Move the legend to the bottom of the figure and change the label of the y-axis.

> **Hint:** Use `aes(x = Year, y = ln_consump_pc, color = Country)` as the mapping for your `ggplot()` to distinguish between countries.

```{r task3}
ts_df <- read.csv("data//ts_data.csv") %>%
  mutate(Year = as.Date(Year)) %>%
  filter(Country == "France" | Country == "Italy", Year >= as.Date("1985-01-01"), Year <= as.Date("2010-01-01")) %>%
  arrange(Year)

ts_df %>%
  ggplot(aes(x = Year, y = ln_consump_pc, color = Country)) +
  geom_line() +
  geom_point() +
  labs(y = "ln(energy consumption per capita)") +
  theme(legend.position = "bottom")
```

## Task 4

1. Read the `cs_data.csv` file and store it as a data frame in your Global Environment.

2. Using the `fixest` package, perform the following three OLS regressions and store each of them in your Global Environment:

    - `wage` on `x1` 

    - `wage` on `x1` and `x2`

    - `wage` on `x1` and `x2` and the categorical variable `nodegree`

3. Present all the models in the same regression table using `huxreg()`. You are not required to perform any additional `huxtable` formatting operations.

```{r huxreg, eval=FALSE}
cs_df <- read.csv("data//cs_data.csv")

model1 <- cs_df %>% feols(wage ~ x1)

model2 <- cs_df %>% feols(wage ~ x1 + x2)

model3 <- cs_df %>% feols(wage ~ x1 + x2 + factor(nodegree))

huxreg(model1, model2, model3)
```

## Submission

Once you have completed all of the tasks successfully, please save and send your final R Script to [wihanmarais@sun.ac.za](mailto:wihanmarais@sun.ac.za) for grading.

