---
title: "Introduction to R: Memorandum"
description: |
  The memorandum for the assignment in "Introduction to R" sessions during the "Intensive Statistics" course for MCom Economics students at the University of Stellenbosch (2023).
date: 2023-01-26
output:
  distill::distill_article:
    self_contained: false
    highlight: breezedark
    highlight_downlit: true
    toc: true
    toc_float: true

---
```{r huxsetup, echo=F}
options("huxtable.knitr_output_format" = "html")
```

## Task 1

A new project or `.Rproj` file can be created in RStudio as follows:

`File > New project > New directory > New project > Choose directory location and name.`

Similarly, a new GitHub document is generated in RStudio as follows:

`File > New file > R Markdown > From template > GitHub Document.`

GitHub Documents typically appear in the wild as `README.Rmd` files employed in GitHub repositories.

## Task 2

The following code chunk is intended to set the default settings for subsequent code chunks and to load the minimum necessary packages using `pacman::p_load()`. Default code chunk settings are set using `knitr::opts_chunk$set()` and most templates are pre-populated with this essential code chunk.

```{r setup}
knitr::opts_chunk$set(
  warning = FALSE,
  echo = TRUE,
  eval = TRUE,
  fig.height = 3.5,
  fig.width = 6
)
source("../scripts/packages.R")

# NB Note to address strange huxtable output
options("huxtable.knitr_output_format" = "html")
# Use this line of code to tell knitr to knit huxtable objects in HTML
```

Which defaults are we setting?

* `warning = FALSE` Prevent warning or error messages from being displayed in the knitted output.
* `echo = TRUE` Show both code and output from chunk in your final product.
* `eval = TRUE` Execute the code written in the chunk.
* `fig.height = 3.5, fig.width = 6` Set the dimensions (in inches) of figures generated in code chunks to $6 \times 3.5$ inches.

## Task 3

```{r task3}
ts_df <- read.csv(file = "../data/ts_data.csv") %>%
  mutate(Year = as.Date(Year, format = "%Y-%m-%d")) %>%
  filter(
    Year >= as.Date("1985-01-01"),
    Year <= as.Date("2010-01-01"),
    Country == "France"
  ) %>%
  arrange(Year)

my_vector <- ts_df %>% pull(ln_consump_pc)

my_adf <- urca::ur.df(
  y = my_vector,
  type = "trend",
  lags = 5,
  selectlags = "AIC"
)

summary(my_adf)
```

## Task 4

```{r task4}
cs_df <- read.csv(file = "../data/cs_data.csv")

model1 <- fixest::feols(wage ~ x1, data = cs_df)

model2 <- fixest::feols(wage ~ x1 + x2, data = cs_df)

model3 <- fixest::feols(wage ~ x1 + x2 + i(treat), data = cs_df)

huxreg(
  "Model 1" = model1, "Model 2" = model2, "Model 3" = model3,
  statistics = c("N" = "nobs", "R-squared" = "r.squared"),
  stars = c(`*` = 0.1, `**` = 0.05, `***` = 0.01, `****` = 0.001),
  number_format = 2,
  coefs = c(
    "Intercept" = "(Intercept)",
    "Explanatory 1" = "x1",
    "Explanatory 2" = "x2",
    "Treatment Received" = "treat::1"
  )
) %>%
  set_font_size(8) %>%
  set_align(8:9, 2:4, value = "center") %>%
  set_caption("Task 4 Regression Table")
```
